---
title: "BDA_Yearly Temperature 2018 - 2019"
author: "Gould, Katelyn"
date: "10/8/2019"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: kable 
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

#Description
In this file I make graph for the change in temperature at two sites over a year from in situ data collected from a (hobo? with make/model) at two sites in Bermuda, Hog Breaker (5-10m) & Hog Beacon (30-35m). This data is being used to support research on bleaching thresholds in bermudian corals across depth.
</br></br>
## What is in this file?
Data cleaning of temperature data
and graph creation using the package "ggplots2" and others
In situ measurements were taken at two reef sites in Bermuda
Hog Breaker (5-10m) from 09/03/2018 through 08/21/2019
Hog Beacon (30-35m) from 09/07/2018 through 08/20/2019
</br></br>


```{r setup, results='hide', message=FALSE}
knitr::opts_chunk$set(echo = TRUE) # will automatically include code in the ouput unless we state otherwise
knitr::opts_chunk$set(warning= FALSE) # will NOT include warning messages in the output unless we state otherwise
# knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE) #keeps code wrapped in the output

# if you haven't installed these packages run the following line (first delete the # sign):
#install.packages(c("tidyverse", "janitor", "kableExtra", "cowplot", "skimr", "measurements"))

library(esquisse)
library(rvg)
#library(ggplot2) # this is a part of tidyverse
#library(plyr) # there are issues w/using plyr and dplyr in the same session, instead of loading plyr just type plyr::function when you want to use a specific function from plyr
#library(tidyr) # this is a part of tidyverse
library(magrittr)
library(tidyverse)
library(lubridate)
library(sf)
library(gridExtra)
library(grid)
library(maps)
library(ggpubr)


```

#Cleaning Data
```{r data inport}
setwd("C:/Github/TPC_BDA_github")

shallowtemp<- read.csv("C:/Github/TPC_BDA_github/Raw_data/HB  Raw Temp data.csv")
deeptemp<- read.csv("C:/Github/TPC_BDA_github/Raw_data/HogBeac_Deep Raw Temp data.csv")

shallowtemp$Site<-  "Shallow"
deeptemp$Site<- "Deep"
mean(shallowtemp$Temp...C.)
mean(deeptemp$Temp...C.)

Alltemp<- rbind(shallowtemp,deeptemp)

#write.csv(Alltemp,"C:/Github/TPC_BDA_github/R_output/Final/Alltemp.csv")

months <- c("December","November","October","September","August","July","June","May","April","March","February","January") ## need this string vector for sorting later



Alltemp$months <- as.Date(Alltemp$Date, format = "%m/%d/%y") %>%
  months() %>%
  as.factor() %>%
  factor(., levels = months)

Alltemp$date <-as.Date(Alltemp$date, format= "%m/%2d/%y")

Alltemp <- janitor::clean_names(Alltemp) #%>%
  #rename(temp= 'temp_u_00b0_c')
#write.csv(Alltemp,"C:/Github/TPC_BDA_github/R_output/Final/Alltempfinal.csv")


```

#Plot 1: Raw temp over time
```{r graph}


raw<-ggplot(Alltemp, aes(x=date, y=temp_c, color=site)) +
  geom_point() +
  theme_classic() +
  labs(x="Date", y=expression(Raw~temp~(degree~C)))

raw + scale_color_manual(breaks = c("Deep", "Shallow"),
                        values= c("blue", "red"))

```
# Mean daily temperatures with sd and Ttest

```{r}
### With SD###
dailymean_sd <- Alltemp %>%
  group_by(site, date) %>%
  mutate(meandaily_temp = round(mean(temp_c), 2), 
         stddev_temp=sd(temp_c))%>%
  distinct(site, date, meandaily_temp, months, stddev_temp)



Deepsd<-subset(dailymean_sd, site =="Deep")
Shallowsd<-subset(dailymean_sd, site =="Shallow")

Tempgra<-ggplot(dailymean_sd, aes(x=site, meandaily_temp, colour= site))+
  stat_boxplot(geom= "errorbar", width= 0.5, position = position_dodge(1))+
  geom_boxplot(position = position_dodge(1))+
  geom_point(aes(fill= months), position = position_jitterdodge(jitter.width = 0, jitter.height = 0))+
  guides(fill= guide_legend(override.aes = list(shape= NA)))+
  theme(panel.background=element_blank(),legend.position = "none") + #to have no gridlines behind graph
  theme(axis.line = element_line(colour = "black")) + #add x and y line
  xlab("Site")+
  ylab("Daily Average Temperature")

boxtemp<-Tempgra+ scale_color_manual(breaks = c("Deep", "Shallow"),values= c("blue", "red"))

Shmon<-Shallowsd%>%
  group_by(months)%>%
  mutate(meanmonth= mean(meandaily_temp),
         monsd= sd(meandaily_temp))%>%
  distinct(site, meanmonth, months, monsd)
  
Demon<-Deepsd%>%
  group_by(months)%>%
  mutate(meanmonth= mean(meandaily_temp),
         monsd= sd(meandaily_temp))%>%
  distinct(site, meanmonth, months, monsd)

monthmena<-rbind(Demon, Shmon)


Meantemp2<-ggplot(dailymean_sd, aes(x= months, y= meandaily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~monthly~temp~(degree~C)))

Meantemp2 + scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))
```

# Max and Min of Shallow/Deep site 

```{r}

MaxShallow<-temp_by_day%>%
#  filter(site!= "Deep")
#MaxDeep<-temp_by_day%>%
#  filter(site!= "Shallow")
#  max(MaxDeep$avg_daily_temp)
#   #27.8929
#MinShallow<-temp_by_day%>%
#  filter(site!= "Deep")
#  min(MinShallow$avg_daily_temp)
#    #18.69223
#  mean(MinShallow$avg_daily_temp)
#  # 23.88372
#MinDeep<-temp_by_day%>%
#  filter(site!= "Shallow")
#  min(MinDeep$avg_daily_temp)
#   #19.47998
#  mean(MinDeep$avg_daily_temp)
#    # 23.16471
  
  Shallow<-Alltemp%>%
  filter(site!= "Deep")
  max(Shallow$temp_c)
  #30.192
  Deep<-Alltemp%>%
  filter(site!= "Shallow")
 
  mean(Shallow$temp_c)
    # 23.27931
  sd(Shallow$temp_c)
      # 3.048
   var(Shallow$temp_c)
      #9.291688
   max(Shallow$temp_c)
     #30.192
  min(Shallow$temp_c)
        #18.461

   mean(Deep$temp_c)
      # 23.42418
   sd(Deep$temp_c)
      #2.396
    var(Deep$temp_c)
      #5.744787
    max(Deep$temp_c)
     #28.692
  min(Deep$temp_c)
      #18.961
 

 


      
  deepvar<-sum((Deep$temp_c-mean(Deep$temp_c))^2)
    #82541.1
  shallvar<-sum((Shallow$temp_c-mean(Shallow$temp_c))^2)
    #199232.4
  (82541.1+199232.4)
  #281773.5
  (206.336/7.869) #F-statistic mean Sq site/mean sw residuals
  pf(26.22138,df1=2,df2=111,lower.tail=F)
#4.716607e-10
  Fitlm<-lm(temp_c~site, Alltemp)
Fitlm
summary(Fitlm)
Anova(Fitlm)
anova(Fitlm)
#3.058e-07


```

#Plot 2: Mean daily temp over time

```{r plot both sites}
#site char to factor
Alltemp$site<-factor(Alltemp$site)


TTtest<-compare_means (temp_c~site, data=Alltemp, method = "t.test")

summary(TTtest)
TTtest
TTtesta<-compare_means (temp_c~site, data=Alltemp, method = "anova")
TTtesta

Fitlm<-lm(temp_c~site, Alltemp)
Fitlm
summary(Fitlm)
anova(Fitlm)

#Fitlm2<-lm(temp_c~site*months, Alltemp)
#Fitlm2
#summary(Fitlm2)
#anova(Fitlm2)
#montemp<-aov(temp_c~site*months, Alltemp)
#summary(montemp)
#TukeyHSD(montemp)

## 8.1e-08 all year temps between shallow and deep
## 3.058e-07 for lm AnoVA
# Currently, each site has multiple temp measurements per day, due to temp being taken at different times. Here I will create a small summary table that we can use for plotting:

temp_by_day <- Alltemp %>%
  group_by(site, date) %>%
  mutate(avg_daily_temp = mean(temp_c)) %>%
  distinct(site, date, avg_daily_temp, months)

# Winter and summer means

winter<- c("November", "December", "January", "February", "March", "April")

summer<- c("May", "June", "July", "August", "September", "October")

### to compare to our temp data for the same months september-december 
### 
winter2<- c("September", "October", "November", "December", "January", "February")

summer2<- c("March", "April", "May", "June", "July", "August")


monthlymean<-temp_by_day%>%
  group_by(site, months)%>%
  mutate(monmean= mean(avg_daily_temp))%>%
  mutate(sd= sd(avg_daily_temp))

monthlymean2<-temp_by_day%>%
  group_by(site, months)

wint<- monthlymean%>%
  filter(months %in% winter)%>%
  summarise(winmean=mean(monmean))

summ<-monthlymean%>%
  filter(months %in% summer)%>%
  summarise(summean=mean(monmean))

wint2<- monthlymean%>%
  filter(months %in% winter2)%>%
  summarise(winmean=mean(avg_daily_temp))

summ2<- monthlymean%>%
  filter(months %in% summer2)%>%
  summarise(summean=mean(avg_daily_temp))

 wint%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(winmean))
 #deep 21.6
  wint%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(winmean))
 #shallow 21.4

 summ%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(summean))
 #deep 25.1
  summ%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(summean))
  #shallow 26.7
  
 wint2%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(winmean))
 #deep 23.6
  wint2%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(winmean))
 #shallow 23.5

summ2%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(summean))
 #deep 23.1
  summ2%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(summean))
  #shallow 24.5
  
  summertemp<- monthlymean%>%
   filter(months== c("May", "June", "July", "August", "September", "October"))
   summertemp2<- monthlymean2%>%
   filter(months== c("March", "April", "May", "June", "July", "August"))

 
 summertemp%>%
 filter(site!= "Shallow")%>%
 summarise(mean= mean(avg_daily_temp))
 #deep 24.68452
 summertemp2%>%
 filter(site!= "Deep")%>%
 summarise(mean= mean(avg_daily_temp))
 #shallow 26.2756
   
Deepsum<-summertemp%>%
  filter(site!= "Shallow")
Shallsum<-summertemp%>%
  filter(site!= "Deep")
Deepsum2<-summertemp2%>%
  filter(site!= "Shallow")
Shallsum2<-summertemp2%>%
  filter(site!= "Deep")



mean(Deepsum$avg_daily_temp)
#24.68452
min(Deepsum$avg_daily_temp)
# 21.27
max(Deepsum$avg_daily_temp)
# 27.36
mean(Deepsum2$avg_daily_temp)
#22.68778
mean(Shallsum$avg_daily_temp)
#26.2756 
min(Shallsum$avg_daily_temp)
# 22.068
max(Shallsum$avg_daily_temp)
# 29.3
mean(Shallsum2$avg_daily_temp)
#24.03289
var(Deepsum$avg_daily_temp)
      #3.226714
var(Deepsum2$avg_daily_temp)
      #4.865735
var(Shallsum$avg_daily_temp)
      #4.902804
var(Shallsum2$avg_daily_temp)
      #11.31614
  deepsumvar<-sum((Deepsum$avg_daily_temp-mean(Deepsum$avg_daily_temp))^2)
  deepsumvar
    #87.12129
  deepsumvar2<-sum((Deepsum2$avg_daily_temp-mean(Deepsum2$avg_daily_temp))^2)
  deepsumvar2
    #136.2406
  shallsumvar<-sum((Shallsum2$avg_daily_temp-mean(Shallsum2$avg_daily_temp))^2)
  shallsumvar
    #132.3757
  shallsumvar2<-sum((Shallsum2$avg_daily_temp-mean(Shallsum2$avg_daily_temp))^2)
  shallsumvar2
    #316.8518
t.test(avg_daily_temp~site,data=summertemp) 
# Welch 2-sample t-test
# t = -2.9528
# df=51.798
# p= 0.004724
t.test(avg_daily_temp~site,data=summertemp2) 

# Welch 2-sample t-test
# t = -1.8007
# df=48.322
# p= 0.07799

Fitsumlm<-lm(avg_daily_temp~site, summertemp)
Fitsumlm
summary(Fitsumlm)
anova(Fitsumlm)
#anova
#df= 54
#f= 8.719
#p= 0.004654

#predlm<- predict(Fitsumlm, interval= "confidence")
#sumCI<-cbind(predlm,summertemp)
Fitsumlm2<-lm(avg_daily_temp~site, summertemp2)
Fitsumlm2
summary(Fitsumlm2)
anova(Fitsumlm2)
#anova
#F=3.243
#DF= 56
#p=0.07714

Meansumtemp<-ggplot(summertemp, aes(x= date, y= avg_daily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~daily~temp~(degree~C)))+ scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))

Meansumtemp
ggexport(Meansumtemp, filename = "Meansumtemp.pdf")

Meansumtemp2<-ggplot(summertemp2, aes(x= date, y= avg_daily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~daily~temp~(degree~C)))+ scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))

Meansumtemp2
ggexport(Meansumtemp2, filename = "Meansumtemp2.pdf")

### winter

wintemp<- monthlymean%>%
   filter(months== c("November", "December", "January", "February", "March", "April"))
wintemp2<- monthlymean2%>%
   filter(months== c("September", "October", "November", "December", "January", "February"))
 
 wintemp%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(avg_daily_temp))

  wintemp%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(avg_daily_temp))
  
 wintemp2%>%
  filter(site!= "Shallow")%>%
  summarise(mean= mean(avg_daily_temp))

  wintemp2%>%
  filter(site!= "Deep")%>%
  summarise(mean= mean(avg_daily_temp))
 
 Deepwin<-wintemp%>%
  filter(site!= "Shallow")

  Shallwin<-wintemp%>%
  filter(site!= "Deep")
  
  Deepwin2<-wintemp2%>%
  filter(site!= "Shallow")

  Shallwin2<-wintemp2%>%
  filter(site!= "Deep")

mean(Deepwin$avg_daily_temp)
#21.607
mean(Deepwin2$avg_daily_temp)
##6 months- 23.61706
mean(Shallwin$avg_daily_temp)
#21.3
mean(Shallwin2$avg_daily_temp)
#6 months- 23.74203
var(Deepwin$avg_daily_temp)
      #2.620888
var(Deepwin2$avg_daily_temp)
     ##6.583108
var(Shallwin2$avg_daily_temp)
      #1.940798
var(Shallwin2$avg_daily_temp)
      #9.484352
  deepwinvar<-sum((Deepwin$avg_daily_temp-mean(Deepwin$avg_daily_temp))^2)
    #76.00576
  deepwinvar2<-sum((Deepwin2$avg_daily_temp-mean(Deepwin2$avg_daily_temp))^2)
    #177.7439
  shallwinvar<-sum((Shallwin$avg_daily_temp-mean(Shallwin$avg_daily_temp))^2)
    #56.2816
  shallwinvar2<-sum((Shallwin2$avg_daily_temp-mean(Shallwin2$avg_daily_temp))^2)
    #265.5619
t.test(avg_daily_temp~site,data=wintemp)
# welch
# t= 0.70701
# df=56.739
# p= 0.4825
t.test(avg_daily_temp~site,data=wintemp2)
# welch
# t= (-0.16667)
# df= (53.862)
# p=(0.8683)
Fitwinlm<-lm(avg_daily_temp~site, wintemp)
Fitwinlm
summary(Fitwinlm)
anova(Fitwinlm)
#F=0.4999
#DF= 58
#p=0.4824
Fitwinlm2<-lm(avg_daily_temp~site, wintemp2)
Fitwinlm2
summary(Fitwinlm2)
anova(Fitwinlm2)
#F=0.0276
#DF=66
#p=0.8687
Meanwintemp<-ggplot(wintemp, aes(x= date, y= avg_daily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~daily~temp~(degree~C)))+ scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))

Meanwintemp
ggexport(Meanwintemp, filename = "Meanwintemp.pdf")

Meanwintemp2<-ggplot(wintemp2, aes(x= date, y= avg_daily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~daily~temp~(degree~C)))+ scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))

Meanwintemp2
ggexport(Meanwintemp2, filename = "Meanwintemp2.pdf")
#### 
Meantemp<-ggplot(temp_by_day, aes(x= date, y= avg_daily_temp)) +
  geom_line(aes(color=site), size= 1.3) +
  theme_classic() +
  labs(x="Date", y=expression(Average~daily~temp~(degree~C)))+ scale_color_manual(breaks = c("Deep", "Shallow"), values= c("blue", "red"))

Meantemp
 
ggexport(Meantemp, filename = "Meantemp.pdf")


temp_by_day%>%
  filter(site!= "Deep")%>%
  summarise(max=max(avg_daily_temp, na.rm=T))
	  #mean max 29.8
 
temp_by_day%>%
  filter(site!= "Shallow")%>%
  summarise(max=max(avg_daily_temp, na.rm=T))
  #mean max 27.9

 mean(Shallowsd$meandaily_temp)
 # Mean Shallow 23.88372
 mean(Deepsd$meandaily_temp)
 	#Mean DEEP 23.16471

```



# Map of Bermuda

```{r}
map.world <- map_data("world")

Atlantic<-map.world%>%
filter(region == c('Bermuda', 'USA'))

# make BDA map
# http://www.diva-gis.org/gdata
aoi_boundary_Bermuda <- st_read("C:/Github/TPC_BDA_github/Raw_data/BMU_adm/BMU_adm0.shp")

berm<-ggplot() + 
  geom_sf(data = aoi_boundary_Bermuda, size = 2, color = "black", fill = "lightblue") + 
  ggtitle("Bermuda") + 
  coord_sf()+
  theme_light()
ggsave('C:/Github/TPC_BDA_github/R_output/berm.png', berm, device = 'png', width = 5, height = 5)

NAO<-ggplot() +
  geom_polygon(data = map.world, aes(x = long, y = lat, group = group))+
  geom_point(x= -64.75, y= 32.3)+
  coord_sf(xlim = c(-100,-40), ylim = c(10,50))+
  xlab("")+
  ylab("")+
  theme_light()
 ggexport(NAO, filename = "NOA.pdf")

 
ggsave('C:/Github/TPC_BDA_github/R_output/NAO.png', NAO, device = 'png', width = 5, height = 5)
```

