---
title: "PI_date_ BDA"
author: "Gould, Katelyn"
date: "10/15/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: kable 
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

#Description
In this file I make the Photosynthsis Irradiance curved based on coral oxygen production rate over incidient light intesnsity (PAR) in corals from two sites in Bermuda, Hog Breaker (5-10m) & Hog Beacon (30-35m). This data is being used to support research on bleaching thresholds in bermudian corals across depth.
</br></br>
## What is in this file?
Data cleaning P/I curve data and curve fittinge
and graph creation using the package "ggplot2" and others
P/I parameter estimates including the compensation point- Irradiance where photosynthesis= 0
Saturation point- maximum rate of photosynthesis (Pmax)
Evidence of photoinhibition- a decrease or plateau in photosynthetic rate after Pmax is reached.
</br></br>


```{r setup, results='hide', message=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_chunk$set(warning= FALSE) 

library(tidyverse)
library(here)
library(readr)
library(ggplot2)
library(esquisse)
library(rvg)
library(minpack.lm)
library(plyr)
library(chron)
library(lubridate)
library(LoLinR)
library(gridExtra)
library(plotrix)
library(segmented)
library(devtools)
library("usethis")
library("rvg")
library("esquisse")
library("here")     
library( "forcats")
library( "stringr")
library( "dplyr")
library(kableExtra)
  
  #[17] "purrr"      "readr"      "tidyr"      "tibble"     "ggplot2"    "tidyverse"  "stats"      "graphics"  
#[25] "grDevices"  "utils"      "datasets"   "methods"    "base"  
```


```{r results='hide', message=FALSE}
#load in data sheet
#
#
#Photo.R <- read.csv("C:/Github/TPC_BDA_github/PI_Curves/PI#_output/Photo.CurveRates_PI.csv")
Photo.R<-read.csv("C:/Github/TPC_BDA_github/PI_Curves/PI_output/Photo.Rlog.csv")
View(Photo.R)
Photo.R$X<-NULL
PIraw<-ggplot(Photo.R, aes(x=avgPAR, y=umol.cm2.hr, col = fragment.ID))+
  geom_point()+  
  ylim(0,1.5)+
  xlab(expression("Photosynthetically Active Radiation ("*mu*"mol photons "*m^-2*s^-1*")"))+
  ylab(expression(Rate* " ("*mu*"mol"*O[2]*""*cm^-2*h^-1*")"))+
  facet_wrap(~treatment)

PIraw

ggplot(Photo.R, aes(x=avgPAR, y=Rate.ln, col = fragment.ID))+
  geom_point()+ 
  xlab(expression("Photosynthetically Active Radiation ("*mu*"mol photons "*m^-2*s^-1*")"))+
  ylab(expression(Rate* " ("*mu*"mol"*O[2]*""*cm^-2*h^-1*")"))+
  facet_wrap(~treatment)
```

# PI CURVE FIT- BDA
#pull out all numerica data point for shallow and deep 

```{r results='hide', message=FALSE}
Photo.Rs<-subset(Photo.R, treatment=="shallow")
View(Photo.Rs)

Photo.RD<-subset(Photo.R, treatment=="deep")
View(Photo.RD)

Shal <- aggregate(umol.cm2.hr ~indPAR, data = Photo.Rs, FUN=mean)
Deep <- aggregate(umol.cm2.hr ~ indPAR, data =  Photo.RD, FUN=mean)
Shal.se <- aggregate(umol.cm2.hr ~ avgPAR, data = Photo.Rs, FUN=std.error)
Deep.se<- aggregate(umol.cm2.hr ~ avgPAR, data = Photo.RD, FUN=std.error)

#light levels used for experiment- All corals were mixed in each trial

light<- mean(c(578, 588, 585, 598, 579, 579, 581, 580))

light.se<-std.error(c(578, 588, 585, 598, 579, 579, 581, 580))

```

# Plot Photosynthetic rate over PAR for Shallow site

```{r}


# seperate PAR and umol.cm2.hr into two data frames
PARs <- as.numeric(Shal$indPAR)

PCs <- as.numeric(Shal$umol.cm2.h)


#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrc= nlsLM(PCs~(1/(2*theta))*(AQY*PARs+Am-sqrt((AQY*PARs+Am)^2-4*AQY*theta*Am*PARs))-Rd,start=list(Am=(max(PCs)-min(PCs)),AQY=0.0001,Rd=-min(PCs),theta=0.5))

my.fit <- summary(curve.nlslrc)
#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters into a table
Shallow.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Shallow.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Shallow.PI.Output

```

```{r results='hide',  message=FALSE}
#Plot input data and model fit
shallowPIC<-plot(PARs,PCs,xlab="", ylab="", xlim=c(0,max(PARs)), ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="A) Hog Beacon", adj = 0.05) #set plot info
segments(PARs,PCs-Shal.se$umol.cm2.hr,PARs,PCs+Shal.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
curve((1/(2*summary(curve.nlslrc)$coef[4,1]))*(summary(curve.nlslrc)$coef[2,1]*x+summary(curve.nlslrc)$coef[1,1]-sqrt((summary(curve.nlslrc)$coef[2,1]*x+summary(curve.nlslrc)$coef[1,1])^2-4*summary(curve.nlslrc)$coef[2,1]*summary(curve.nlslrc)$coef[4,1]*summary(curve.nlslrc)$coef[1,1]*x))-summary(curve.nlslrc)$coef[3,1],lwd=2,col="Red",add=T)
abline(v=Shallow.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
#text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="blue", lty=3, lwd = 3)
#text(x =250, y = 1.5, label = "Ik", srt = 0)

#plot(PARs,PCs,xlab="", ylab="", xlim=c(0,max(PARs)), #ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="A) Shallow", #adj = 0.05) #set plot info
#segments(PARs,PCs-Shal.se$umol.cm2.hr,PARs,PCs+Shal.se$umol.cm2#.hr)
#mtext(expression("Irradiance ("*mu*"mol photons #"*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
#mtext(expression(Rate*" ("*mu*"mol "*O[2]*" #"*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
##draw the curve using the model fit
#curve((1/(2*summary(curve.nlslrc)$coef[4,1]))*(summary(curve.nl#slrc)$coef[2,1]*x+summary(curve.nlslrc)$coef[1,1]-sqrt((summary#(curve.nlslrc)$coef[2,1]*x+summary(curve.nlslrc)$coef[1,1])^2-4#*summary(curve.nlslrc)$coef[2,1]*summary(curve.nlslrc)$coef[4,1#]*summary(curve.nlslrc)$coef[1,1]*x))-summary(curve.nlslrc)$coe#f[3,1],lwd=2,col="Red",add=T)
#abline(v=Shallow.PI.Output[5], col="gray", lty = 2)
#abline(v=light, col="black", lty = 2) #add line for TPC light #level
#text(x =650, y = 1.5, label = "TPC light", srt = 0)
## add a line to figure for the Ik or saturation point 
#abline(v=Ik, col="blue", lty=3, lwd = 3)
#text(x =250, y = 1.5, label = "Ik", srt = 0)


```

# Plot Photosynthetic rate over PAR for DEEP site

```{r include=false,  message=FALSE}

dev.off()

# seperate PAR and umol.cm2.hr into two data frames
PARd <- as.numeric(Deep$indPAR)

PCd <- as.numeric(Deep$umol.cm2.h)


#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrcd= nlsLM(PCd ~ (1/(2*theta))*(AQY*PARd +Am-sqrt((AQY*PARd +Am)^2-4*AQY*theta*Am*PARd ))
                  -Rd,start=list(Am=(max(PCd)-min(PCd)),AQY=0.0001,Rd=-min(PCd),theta=0.4))

my.fit <- summary(curve.nlslrcd)


#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters into a table
Deep.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Deep.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Deep.PI.Output


```

```{r include=false,  message=FALSE}
#Plot input data and model fit
plot(PARd ,PCd,xlab="", ylab="", xlim=c(0,max(PARd )), ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="B) Deep Baby", adj = 0.05) #set plot info
segments(PARd ,PCd-Deep.se$umol.cm2.hr,PARd ,PCd+Deep.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
#hyperbolic tangent, more common way to fit 
curve((1/(2*summary(curve.nlslrcd)$coef[4,1]))*(summary(curve.nlslrcd)$coef[2,1]*x+summary(curve.nlslrcd)$coef[1,1]-sqrt((summary(curve.nlslrcd)$coef[2,1]*x+summary(curve.nlslrcd)$coef[1,1])^2-4*summary(curve.nlslrcd)$coef[2,1]*summary(curve.nlslrcd)$coef[4,1]*summary(curve.nlslrcd)$coef[1,1]*x))-summary(curve.nlslrcd)$coef[3,1],lwd=2,col="blue",add=T)
abline(v=Deep.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
#text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="red", lty=3, lwd = 3)
#text(x =150, y = 1.5, label = "Ik", srt = 0)

```

## By Species DLAB

```{r include=false,  message=FALSE}
Dlab <- (subset(Photo.R,species== "DLAB", avgPAR & umol.cm2.hr))

PARdlab <- as.numeric(Dlab$indPAR)

PCdlab <- as.numeric(Dlab$umol.cm2.h)

DlabP <- aggregate(umol.cm2.hr ~ indPAR, data =  Dlab, FUN=mean)
DlabP.se<- aggregate(umol.cm2.hr ~ avgPAR, data = Dlab, FUN=std.error)

#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrcdlab= nlsLM(PCdlab ~ (1/(2*theta))*(AQY*PARdlab +Am-sqrt((AQY*PARdlab +Am)^2-4*AQY*theta*Am*PARdlab ))
                  -Rd,start=list(Am=(max(PCdlab)-min(PCdlab)),AQY=0.0001,Rd=-min(PCdlab),theta=0.4))


my.fit <- summary(curve.nlslrcdlab)
#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters intol a table
Dlab.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Dlab.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Dlab.PI.Output


```

```{r include=false,  message=FALSE}
#Plot input data and model fit
plot(PARdlab ,PCdlab,xlab="", ylab="", xlim=c(0,max(PARdlab )), ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="DLAB", adj = 0.05) #set plot info
segments(PARdlab ,PCdlab-DlabP.se$umol.cm2.hr,PARdlab ,PCdlab+DlabP.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
#hyperbolic tangent, more common way to fit 
curve((1/(2*summary(curve.nlslrcdlab)$coef[4,1]))*(summary(curve.nlslrcdlab)$coef[2,1]*x+summary(curve.nlslrcdlab)$coef[1,1]-sqrt((summary(curve.nlslrcdlab)$coef[2,1]*x+summary(curve.nlslrcdlab)$coef[1,1])^2-4*summary(curve.nlslrcdlab)$coef[2,1]*summary(curve.nlslrcdlab)$coef[4,1]*summary(curve.nlslrcdlab)$coef[1,1]*x))-summary(curve.nlslrcdlab)$coef[3,1],lwd=2,col="blue",add=T)
abline(v=Dlab.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="red", lty=3, lwd = 3)
text(x =100, y = 1.5, label = "Ik", srt = 0)

```

## By Species MCAV

```{r include=false,  message=FALSE}



Mcav <- (subset(Photo.R,species== "MCAV", avgPAR & umol.cm2.hr))

PARMcav <- as.numeric(Mcav$indPAR)

PCMcav <- as.numeric(Mcav$umol.cm2.h)

McavP <- aggregate(umol.cm2.hr ~ indPAR, data =  Mcav, FUN=mean)
McavP.se<- aggregate(umol.cm2.hr ~ avgPAR, data = Mcav, FUN=std.error)

#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrcMcav= nlsLM(PCMcav ~ (1/(2*theta))*(AQY*PARMcav +Am-sqrt((AQY*PARMcav +Am)^2-4*AQY*theta*Am*PARMcav ))
                  -Rd,start=list(Am=(max(PCMcav)-min(PCMcav)),AQY=0.0001,Rd=-min(PCMcav),theta=0.3))


my.fit <- summary(curve.nlslrcMcav)
#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters intol a table
Mcav.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Mcav.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Mcav.PI.Output


```

```{r include=false,  message=FALSE}
#Plot input data and model fit
plot(PARMcav ,PCMcav,xlab="", ylab="", xlim=c(0,max(PARMcav )), ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="MCAV", adj = 0.05) #set plot info
segments(PARMcav ,PCMcav-McavP.se$umol.cm2.hr,PARMcav ,PCMcav+McavP.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
#hyperbolic tangent, more common way to fit 
curve((1/(2*summary(curve.nlslrcMcav)$coef[4,1]))*(summary(curve.nlslrcMcav)$coef[2,1]*x+summary(curve.nlslrcMcav)$coef[1,1]-sqrt((summary(curve.nlslrcMcav)$coef[2,1]*x+summary(curve.nlslrcMcav)$coef[1,1])^2-4*summary(curve.nlslrcMcav)$coef[2,1]*summary(curve.nlslrcMcav)$coef[4,1]*summary(curve.nlslrcMcav)$coef[1,1]*x))-summary(curve.nlslrcMcav)$coef[3,1],lwd=2,col="blue",add=T)
abline(v=Mcav.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="red", lty=3, lwd = 3)
text(x =100, y = 1.5, label = "Ik", srt = 0)

```


## By Species OFRA

```{r include=false,  message=FALSE}



Ofra <- (subset(Photo.R,species== "OFRA", avgPAR & umol.cm2.hr))

PAROfra <- as.numeric(Ofra$indPAR)

PCOfra <- as.numeric(Ofra$umol.cm2.h)

OfraP <- aggregate(umol.cm2.hr ~ indPAR, data =  Ofra, FUN=mean)
OfraP.se<- aggregate(umol.cm2.hr ~ avgPAR, data = Ofra, FUN=std.error)

#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrcOfra= nlsLM(PCOfra ~ (1/(2*theta))*(AQY*PAROfra +Am-sqrt((AQY*PAROfra +Am)^2-4*AQY*theta*Am*PAROfra ))
                  -Rd,start=list(Am=(max(PCOfra)-min(PCOfra)),AQY=0.0001,Rd=-min(PCOfra),theta=0.3))


my.fit <- summary(curve.nlslrcOfra)
#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters intol a table
Ofra.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Ofra.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Ofra.PI.Output


```

```{r include=false,  message=FALSE}
#Plot input data and model fit
plot(PAROfra ,PCOfra,xlab="", ylab="", xlim=c(0,max(PAROfra )), ylim=c(0,1.55),cex.lab=0.8,cex.axis=0.8,cex=1,main="OFRA", adj = 0.05) #set plot info
segments(PAROfra ,PCOfra-OfraP.se$umol.cm2.hr,PAROfra ,PCOfra+OfraP.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
#hyperbolic tangent, more common way to fit 
curve((1/(2*summary(curve.nlslrcOfra)$coef[4,1]))*(summary(curve.nlslrcOfra)$coef[2,1]*x+summary(curve.nlslrcOfra)$coef[1,1]-sqrt((summary(curve.nlslrcOfra)$coef[2,1]*x+summary(curve.nlslrcOfra)$coef[1,1])^2-4*summary(curve.nlslrcOfra)$coef[2,1]*summary(curve.nlslrcOfra)$coef[4,1]*summary(curve.nlslrcOfra)$coef[1,1]*x))-summary(curve.nlslrcOfra)$coef[3,1],lwd=2,col="blue",add=T)
abline(v=Ofra.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="red", lty=3, lwd = 3)
text(x =100, y = 1.5, label = "Ik", srt = 0)

```


## By Species PAST
 
```{r include=false,  message=FALSE}



Past <- (subset(Photo.R,species== "PAST", avgPAR & umol.cm2.hr))

PARPast <- as.numeric(Past$indPAR)

PCPast <- as.numeric(Past$umol.cm2.h)

PastP <- aggregate(umol.cm2.hr ~ indPAR, data =  Past, FUN=mean)
PastP.se<- aggregate(umol.cm2.hr ~ avgPAR, data = Past, FUN=std.error)

#fit a model using a Nonlinear Least Squares regression of a non-rectangular hyperbola (Marshall & Biscoe, 1980)
curve.nlslrcPast= nlsLM(PCPast ~ (1/(2*theta))*(AQY*PARPast +Am-sqrt((AQY*PARPast +Am)^2-4*AQY*theta*Am*PARPast ))
                  -Rd,start=list(Am=(max(PCPast)-min(PCPast)),AQY=0.0001,Rd=-min(PCPast),theta=0.3))


my.fit <- summary(curve.nlslrcPast)
#summary of model fit


#Amax (max gross photosytnthetic rate)

Pmax.gross <- my.fit$parameters[1]


#AQY (apparent quantum yield) alpha

AQY <- my.fit$parameters[2]


#Rd (dark respiration)

Rd <- my.fit$parameters[3]


# Ik light saturation point

Ik <- Pmax.gross/AQY

# Ic light compensation point
Ic <- Rd/AQY

# Net photosynthetic rates
Pmax.net <- Pmax.gross - Rd


#output parameters intol a table
Past.PI.Output <- rbind(Pmax.gross, Pmax.net, -Rd, AQY,Ik,Ic)
row.names(Past.PI.Output) <- c("PGross.max","Pnet.max","Rdark","alpha", "Ik", "Ic")
Past.PI.Output


```

```{r include=false,  message=FALSE}
#Plot input data and model fit
plot(PARPast ,PCPast,xlab="", ylab="", xlim=c(0,max(PARPast )), ylim=c(0,1.5),cex.lab=0.8,cex.axis=0.8,cex=1,main="PAST", adj = 0.05) #set plot info
segments(PARPast ,PCPast-PastP.se$umol.cm2.hr,PARPast ,PCPast+PastP.se$umol.cm2.hr)
mtext(expression("Irradiance ("*mu*"mol photons "*m^-2*s^-1*")"),side=1,line=3.3,cex=1) #add labels
mtext(expression(Rate*" ("*mu*"mol "*O[2]*" "*cm^-2*h^-1*")"),side=2,line=2,cex=1) #add labels
#draw the curve using the model fit
#hyperbolic tangent, more common way to fit 
curve((1/(2*summary(curve.nlslrcPast)$coef[4,1]))*(summary(curve.nlslrcPast)$coef[2,1]*x+summary(curve.nlslrcPast)$coef[1,1]-sqrt((summary(curve.nlslrcPast)$coef[2,1]*x+summary(curve.nlslrcPast)$coef[1,1])^2-4*summary(curve.nlslrcPast)$coef[2,1]*summary(curve.nlslrcPast)$coef[4,1]*summary(curve.nlslrcPast)$coef[1,1]*x))-summary(curve.nlslrcPast)$coef[3,1],lwd=2,col="blue",add=T)
abline(v=Past.PI.Output[5], col="gray", lty = 2)
abline(v=light, col="black", lty = 2) #add line for TPC light level
text(x =650, y = 1.5, label = "TPC light", srt = 0)
# add a line to figure for the Ik or saturation point 
abline(v=Ik, col="red", lty=3, lwd = 3)
text(x =100, y = 1.5, label = "Ik", srt = 0)

```

#tables

```{r include=false,  message=FALSE}

# Use the kableExtra package to view a pretty table for a subset of the data:
  # First, let's just subset the first 10 rows
Shallow.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="Shallow PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

Deep.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="Deep PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

Dlab.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="DLAB PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

Mcav.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="MCAV PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

Ofra.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="OFRA PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 

Past.PI.Output %>% 
    # Add a title
  kableExtra::kable(caption="PAST PI Parameters") %>% 
    # Specify how we will see the table, type ?kablestyling to see explanations and options
  kable_styling(bootstrap_options = "condensed", full_width=F) 



```




